\begin{center}
\textbf{\textit{\large{Acknowledgements}}}
\end{center}

There is no proper words for me to express my deep gratitude toward my thesis advisor, Professor Eunseo Choi. He has changed my life in a very positive way. From him, I have learned what a great researcher and educator should be like. It is because of his unfailing care and understanding that have given me the courage to persevere, and to carry on during the darkest days as an international student far away from home. It is his vivid and interesting lessons that have inspired me so much that I want to devote my career into geodynamic modeling. It is his numerous inspiration and encouragement that has motivated me to work super hard (enjoy at the same time) on the fascinating research questions. It is his altruistic share that has provided me with great chances to learn from outstanding researchers, references, and to attend meetings. It is his patience to guide me through my endless silly questions that has nurished and cultivated my capabilities of being an independent researcher. Blessings from Eunseo, my role model, are countless. I will keep them in mind and try my best to relay the torch.
\\
I would also like to thank members of my thesis committee, Professor Christine Powell and Professor Jer-Ming Chiu, for their guidance and support. Especially I want to thank Dr. Chiu for his sharing and advice on my course term projects and for his patience to answer all my silly questions. In addition, I want to thank Dr. Powell for your warmhearted encouragement and benevolence during my studies at the Center for Earthquake Research and Information (CERI). 
\\
My sincere thanks must also go to the CERI and the University of Memphis (UM). Thanks a lot for providing me this great chance to study here with full tuition and graduate research assistanship. It is this kind support that has made my two-year studies at this great institution possible. 
\\
I am also grateful to the courses instructors for many vivid and interesting courses that have stimulated my interests in Geophysics, helped me build up my foundation and expanded my horizon in the field. They are Professor Robert Smalley for ``Data Analysis in Geophysics'', Professor Charles Langston for ``Global Seismology'' and ``Inverse Methods in Geophysics'', Professor Mitch Withers for ``Signal Processing in Earth Science'', Professor Eunseo Choi for ``Global Geophysics'' and ``Geodynamics'', Professor Christine Powell for ``Evironmental Geophysics'', Professor Randy Cox for ``Art of Earth Science'', Professor Jer-Ming Chiu for ``Exploration Seismology''. Thank you so much. Especially, I want to thank Professor Withers for you encouragement and your time and efforts for answering all my questions. I would also like to thank Professor Eric Daub for your delicious homemade cakes provdided to us graduate students every Wednesday during the ``CERI Discussion''. I am probably the person who ate the most of them and enjoyed the most.
\\
Many thanks must also go to my dear classmates and research colleagues, with whom, I have lived, studied and worked during the two years. Especially, I want to thank Yang Yang for your supportive help and share on my term projects. Thank you for being a wonderful roommate. I would also like to thank my best ``cubic office mate'', Naeem Khoshnevis, for his best company. We've been studied together as the most diligent (long staying) people in CERI (12/7). Thank you for those benevolent and uncountable ``how are you'', ``good morning'', ``good night'' as well as many good chats. My sincere thanks must also go to Sabber Ahamed, who has been encouraging me during my darkest days when I lost direction. It is his enthusiastic share and encouragement that have helped me go through the bad days. 
\\
Many thanks must also go to CERI staffs. Thank you Chris McGoldrick for many of your kindly help and all the nice chats, from which I have learned many new English words and phrases. Thank you Tanya Broadbent and Kathleen Tucker for sending me birthday gifts which makes me feel so warm as being a member of CERI families. Thank you Christy Chiu and Jer-Ming Chiu for inviting me to your house for Chineses Spring Festival lunch which helped a lot in soothing my nostalgia for hometown. Thank you Gary Patterson for your share and benevolence. Thank you Deshone Marshall for constantly helping me out in using CERI's lab computers. Thank you Josephine Calhoun for providing us tidy and enjoyable environments for studying and doing research everyday. 
\\
I also want to sincerely thank Center for Writing and Communication of the UM. Especially, I want to thank Bill Schraufnagel for your very supportive helps on revising this thesis and enhancing the presentation.
\\
I am also thankful to many great researchers that have encouraged and inspired me for this research. Thank you Professor Lin, Jian for your encouragement during 2014 AGU fall meeting. Thank you Jean-Arthur Olive for your feedback and your kind share. Thank you Professor Taras Gerya for your feedback and your great book \textit{Introduction to Numerical Geodynamic Modelling} that has inspired me a lot. Thank you Professor Suzanne Carbotte for your share and encouragement. Thank you Professor Roger Buck for several inspiring talks and sharing as well as feedbacks on this research.
\\
I also want to thank Professor Liu, Jie (\begin{CJK}{UTF8}{gbsn}刘洁\end{CJK}) and Professor Zhang, Ke (\begin{CJK}{UTF8}{gbsn}张珂\end{CJK}) from Sun Yat-sen University, for kindly sharing your computing resourses on Tianhe2 to me. Many thanks must also go to the staffs of Penguin, Stampede and Tianhe2 supercomputer centers, thank you so much for all the technical supports. Especially, I would like to thank National Supercomputer Center in Guangzhou, China, for providing me surpports with more than 200k of core-hours. 
\\
Sincere thanks must also go to the lifeguards and staffs of the swimming pool of the UM Recreation Center. Thank you for your work in providing me such a safe and enjoyable workout environments. Thank you for accompanying me almost everyday and making sure my safty during I am swimming. I could not endure all the stresses from the high pressure school works if without being able to enjoy swimming everyday.  
\\
In addition, I also want to express my sincere thank to Professor Cheng, Gu (\begin{CJK}{UTF8}{gbsn}成谷\end{CJK}), my undergraduate thesis advisor. Thank you for providing me a chance to start my career as a geophysicist. Thank you for all your guidance and share. 
\\
I should never forget my deep gratitude to my middle school Math teacher Feng, Yan (\begin{CJK}{UTF8}{gbsn}冯艳\end{CJK}) and high school Math teacher Chen, Shengfang (\begin{CJK}{UTF8}{gbsn}陈胜方\end{CJK}) and Physics teacher Lyu, Lijie (\begin{CJK}{UTF8}{gbsn}吕黎洁\end{CJK}) as well as English teacher Cindy (\begin{CJK}{UTF8}{gbsn}叶晓靖\end{CJK}). It is your great education, inspiration, love and care that have cultivated me into a person, who begins able to appreciate the fascinating science world. Your great efforts and patience in teaching me and answering my silly questions have helped me build up a good foundation for my future studies as a science major student.
\\
Special thanks must also go to a special person, Zhang, Siwan (\begin{CJK}{UTF8}{gbsn}张思婉\end{CJK}). Thank you for planted a seed of love and beauty deeply in my heart that has been encouraging and inspiring me through time.    
\\
Finally, I want to thank my families. There simply is no proper word for expressing my gratitude. Thank you so much my dear grandfather Tian, Shengheng (\begin{CJK}{UTF8}{gbsn}田升恒\end{CJK}), and grandmother Wang, Defen (\begin{CJK}{UTF8}{gbsn}王德芬\end{CJK}), who have reared me up with great love and care. Thank you so much my grandgrandfather Tian, Guangzong (\begin{CJK}{UTF8}{gbsn}田光宗\end{CJK}). I will never forget your last words for encouraging me to be a good person and a diligent student.

Thank you my dear mother, Tian, Xia (\begin{CJK}{UTF8}{gbsn}田霞\end{CJK}). You are always a great mother to me. Thank you so much for rearing me up by yourself with your great courage, optimism, love and care. Without you, there is no me.
